Empirical Evaluation of eval in R

### 2020-08-28 inst/analysis/counts.Rmd
fixed table 2

eval_callsite_table3 <- map_dfc(seq(1, nrow(eval_callsite_table), eval_callsite_table_row), function(i) {
  x <- tibble(
    eval_callsite_table[i:(i+eval_callsite_table_row), "site_count"],
    eval_callsite_table[i:(i+eval_callsite_table_row), "package_count"]
  )
  colnames(x) <- paste0(colnames(x), i)
  x
})
rownames(eval_callsite_table3) <- NULL

>>>>

eval_callsite_table3 <- map_dfc(seq(1, nrow(eval_callsite_table), eval_callsite_table_row), function(i) {
  x <- tibble(
    eval_callsite_table[i:(i+eval_callsite_table_row-1), "site_count"],
    eval_callsite_table[i:(i+eval_callsite_table_row-1), "package_count"]
  )
  colnames(x) <- paste0(colnames(x), i)
  x
})
rownames(eval_callsite_table3) <- NULL
